### 2023-03-13 main/chapter_2ljets.tex
write about simulation

@@

>>>>

Throughout $\twoljets$-electroweak, simulated Monte Carlo samples are the
primary estimates of background and signal processes.
We first simulate samples at `truth-level' by random sampling from
distributions that are implemented by various software packages to approximate
theoretical predictions from quantum field theory.
Simulating events from high-order perturbative quantum field theory is
difficult and computationally expensive, so these implementations use
lower-order approximations, which we normalize to cross-section predictions
that are evaluated at higher precision.
Parton shower programs are used to model the soft QCD evolution of
strongly-interacting particles from the hard scatter down to the low energy
scales of hadronization; because of colour confinement, only these
(colour-neutral) hadrons can survive to interact with the detector.
The various Monte Carlo simulation programs used in this search are summarized
in Table~\ref{tab:2ljets_paper_mc}, which is adapted from the $\twoljets$
paper.
Truth-level results are finally passed through a full simulation of the
\atlas\ detector to simulate `reconstruction-level'
data~\cite{SOFT-2010-01, geant2003}.

@@

\begin{table}[tp]
\begin{center}
\scriptsize
\begin{tabular}{l l l l l l }
% \hline
% Physical process &  Generator  & Parton & Cross-section & Tune & PDF set\\
%                 &             & shower & order in pQCD &      & \\
% %\hline\hline
% \noalign{\smallskip}\hline\noalign{\smallskip}
% \ttbar~\cite{ATL-PHYS-PUB-2016-004}         & \POWHEGBOX[v2] \cite{Nason:2004rx,Frixione:2007vw,Alioli:2010xd}    & \Pythia[8.230] \cite{Sjostrand:2014zea} & NNLO+NNLL \cite{ttbarxsec1,ttbarxsec2,ttbarxsec3,ttbarxsec4,ttbarxsec5}                   & A14 \cite{ATL-PHYS-PUB-2014-021}   & \textsc{NNPDF2.3lo} \cite{Ball:2012cx}\\
% $Wt$~\cite{ATL-PHYS-PUB-2016-004}  & \POWHEGBOX[v2]    & \Pythia[8.230] & NNLO+NNLL \cite{Kidonakis:2010b,Kidonakis:2010tc,Kidonakis:2011wy,Frederix:2012dh}        &A14    & \textsc{NNPDF3.0nlo} \cite{Ball:2014uwa}\\
% $VV$~\cite{ATL-PHYS-PUB-2016-002} & \Sherpa[2.2.2] \cite{Bothmann:2019yzt} & \Sherpa[2.2.2] & NLO \cite{diboson1,diboson2} & \textsc{Sherpa}\ default & \textsc{NNPDF3.0nnlo} \\
% $Z/\gamma^{*}(\rightarrow \ell \ell)$\,+\,jets~\cite{ATL-PHYS-PUB-2016-003}& \Sherpa[2.2.1]           & \Sherpa[2.2.1]  &NNLO \cite{DYNNLO1,DYcrosssection}       & \textsc{Sherpa}\ default     &\textsc{NNPDF3.0nnlo}\\
% Higgs ($t\bar{t}H$) & \POWHEGBOX[v2]    & \Pythia[8.230] & NLO \cite{deFlorian:2016spz} & A14    & \textsc{NPDF2.3lo}\\
% Higgs (VBF, $Vh$) & \POWHEGBOX[v2]     & \Pythia[8.212] & NNLO \cite{deFlorian:2016spz} & AZNLO \cite{STDM-2012-23} &  \textsc{CTEQ6L1} \cite{Pumplin:2002vw} \\
% Higgs (ggF) & \POWHEGBOX[v2]     & \Pythia[8.212] & NNNLO \cite{deFlorian:2016spz} & AZNLO & \textsc{CTEQ6L1} \\
% $ttt$, $tttt$, $t\bar{t}$\,+\,$WW$ & \textsc{MG5\_aMC@NLO} \cite{Alwall:2014hca} & \Pythia[8.186] \cite{Skands:2014pea} & NLO \cite{Frederix:2017wme}, \cite{Alwall:2014hca} & A14 & \textsc{NNPDF2.3lo}\\
% $t\bar{t}$\,+\,$V$~\cite{ATL-PHYS-PUB-2016-005,Garzelli:2012bn}& \textsc{MG5\_aMC@NLO}        & \Pythia[8.210] & NLO \cite{Campbell:2012,Lazopoulos:2008,Alwall:2014hca} & \textsc{A14} & \textsc{NNPDF2.3lo}\\
% $VVV$~\cite{ATL-PHYS-PUB-2016-002} & \Sherpa[2.2.2] & \Sherpa[2.2.2] &  NLO \cite{Bothmann:2019yzt} & \textsc{Sherpa}\ default     & \textsc{NNPDF3.0nnlo}\\
% \noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular}
\caption{%
Caption TODO
% TODO rewrite
% Simulated background event samples used in this analysis with the corresponding matrix element and parton shower generators,
% cross-section order in perturbative QCD used to normalize the event yield, underlying-event tune and PDF set.
% $V$ represents either a $W$ or $Z$ boson.%
}
\label{tab:2ljets_paper_mc}
\end{center}
\end{table}
